\section{Introduction}
The Bachelor's advanced physics laboratory at RWTH Aachen University is offered annually to upper division physics students, typically in their final year of physics study.
This laboratory serves roughly 150 students during each offering.
The laboratory is structured largely into two halves.
During the first half of the semester students attend a series of 12 lectures on high energy physics (HEP) detector topics and 12 lectures on solid state physics (SSP)detector topics.
During the second half of the semester students, in pairs of groups of 2 or three students each, perform 5-7 experiments.
These experiments are selected from a set of approximately 25 available experiments of which roughly half are from HEP topics and the other half from SSP topics.
The experiments that the students perform range from classical large-scale experiments such as the Stern-Gerlach experiment to more complex and modern topics such as the gas electron multiplier experiment.


The structure of the experimental portion of each laboratory experiment is broken into three primary parts: discussion, experiment, and report.
Students are expected to have attended the appropriate lecture during the first half of the class as well as to have read the experiment manual prior to performing the experiment.
As such, students are to respond verbally to questions pertaining to the physics theory and electronics hardware operation outlined in the manual and lecture.
An experiment supervisor asks the students the discussion questions in a free response format.
If the students do not demonstrate the minimum level of understanding required to safely perform the experiment, the students are asked to return after reviewing the material further, at which point they are questioned again.
The experiment supervisor then explains, and if necessary demonstrates, any part of the experiment that might be easily damaged, or require special care not described in the manual.
From this point, the students are left to perform the experiment and collect data as outlined in the lab manual.
If the students have questions, encounter problems, or otherwise need to speak to the supervisor, they meet with him as needed.
Lastly, within two weeks of completing the experiment, the students are expected to submit a formal lab report which should take a form similar to that of a typical physics paper.

This paper details some of improvements that were implemented into the advanced physics laboratory course.
In section 2 we motivate these improvements.
In sections 3, 4, and 5, we give detailed descriptions of the portion of experiments that were modified, discussing why the portions were modified and what changes were implemented.
In section 6 we discuss some conclusions found and general student feedback collected following implementation.
